Index measures for oak decline severity using phenotypic descriptors

### 2020-02-18 manuscript/manuscript.Rmd
added size adjusted site differences figure to supplementary. Altered figure references accordingly

A scatter plot (Figure 1) of the calculated PDI and DAI scores (see Supplementary information Figures 4 to 7) for all `r nrow(site_corrected_analysis_suitable_data)` trees for which phenotypic descriptor data was collected shows that the healthy trees group towards the lower end of the PDI scale and the symptomatic COD and AOD groups towards the higher end.
This gave a significant difference when PDI of the control and symptomatic (AOD and COD) decline statuses were compared using an independent two sample t-test (`r glue("t({PDI_status_ttest$parameter}) = {signif(PDI_status_ttest$statistic,digits = 3) %>% abs()}, p < 0.001")`) with group means of `r signif(PDI_status_ttest$estimate1,digits = 3)` and `r signif(PDI_status_ttest$estimate2,digits = 3)` for non-symptomatic and symptomatic statuses respectively.

@@

Plots of the individual descriptors against the decline indexes are available in Supplementary Figures 4-7. 
The following sections identify how the descriptors contribute and interact within the decline index models in specific decline cases.

>>>>

A scatter plot (Figure 1) of the calculated PDI and DAI scores (see Supplementary information Figures 5 to 8) for all `r nrow(site_corrected_analysis_suitable_data)` trees for which phenotypic descriptor data was collected shows that the healthy trees group towards the lower end of the PDI scale and the symptomatic COD and AOD groups towards the higher end.
This gave a significant difference when PDI of the control and symptomatic (AOD and COD) decline statuses were compared using an independent two sample t-test (`r glue("t({PDI_status_ttest$parameter}) = {signif(PDI_status_ttest$statistic,digits = 3) %>% abs()}, p < 0.001")`) with group means of `r signif(PDI_status_ttest$estimate1,digits = 3)` and `r signif(PDI_status_ttest$estimate2,digits = 3)` for non-symptomatic and symptomatic statuses respectively.

@@

Plots of the individual descriptors against the decline indexes are available in Supplementary Figures 5-8. 
The following sections identify how the descriptors contribute and interact within the decline index models in specific decline cases.
